The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2023-06-29 donde.tex
add row to hit-miss table for chocie rule & text editing

\title{The controlled choice design and private paternalism in pawnshop borrowing\thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting. Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM, USC, and UCSD provided valuable feedback.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira: ITAM/MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
\date{This draft:  \today \\[2 cm]}

@@

Substantiating a case for private paternalism is not easy. It involves comparing the causal effect of forcing a certain product characteristic versus the effect of letting people choose it. This is not a straightforward task because choice will be driven by unobservable factors, and to address the question fully we would want a counterfactual for the outcome of both choosers and non-choosers. A large behavioral literature has illustrated that allowing borrowers or savers to choose commitment-style products increase savings in an Intention-to-Treat sense \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, but this literature has rarely inquired about the benefits of imposing commitment.\footnote{Selection on gains has such wide acceptance that economists often impose it in their models (for example, in the study of migration \cite{chiquiar2005international} and occupational choice \cite{heckman1990empirical}. In microfinance, a context close to ours, \citep{Murdoch} claims that positive selection exists, citing a positive correlation between displaying present biased preferences in surveys and selecting into microfinance as evidence of borrowers' actually demanding the discipline imposed by frequent payments.}   In this paper we illustrate how a three-armed, `controlled choice' design can be used to form counterfactuals for both choosers and non-choosers of commitment, providing a high-stakes and policy-relevant environment in which to test selection-on-gains as well as isolating the impact of paternalistic policies.

@@

Here we study the benefits of private paternalism in the context of pawnbroker lending. Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing \citep{carter2012pawnshops}. There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a 43 billion dollar industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} Pawnshop lending presents an inverted lending case: since these loans are over-capitalized, the principal in the lending contract stands to gain the most when agents default.

Our collaborating pawn lender (henceforth Lender P) gave 70\% of the value of the pawn in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract typical of the industry that can be paid back anytime before the loan comes due at no penalty. This combination of features, and the fact that the gold pawn is highly liquid, means that the lender makes 90\% more profit over three months for a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid). While an older literature considers the exploitative potential in over-collateralization and underpricing of collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.  %When the lender desires default, the repayment-inducing features of commitment-style repayment contracts become undesirable and there may be incentives for the principal to create contracts with no structure, no reminders, and simple balloon payments. 
To repurpose the language of \cite{Laibson2018}, we suggest that pawn contracts effectively shroud their \textit{lack} of commitment features to induce default in a manner not obvious to borrowers. Given that pawnshops, moneylenders, and paycheck lending institutions are likely to face client pools disproportionately made up of impatient and time-inconsistent individuals, the design of such contracts may have serious consequences for the financial lives of the poor.

@@

Against this backdrop, we implement a multi-arm randomized control trial covering close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City, using a design built to test the demand for and impact of payment structure in pawn repayment contracts. Our control arm illustrates the costs of the status quo contract; fully 57\% of borrowers default and so lose their pawn.\footnote{These high default rates are not uncommon, in the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).} We then implement a `commitment choice’ arm, in which borrowers are able at the time of taking a loan to opt in to a structured repayment contract, in which they are asked to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time, and borrowers levied a nominal fee of 2\% of that month's payment in case of delinquency as a reminder/reinforcement of the importance of these interim payments. In addition, we include a `forced commitment’ arm, in which all borrowers are required to repay using the monthly payment structure.

We call this randomization of voluntary and forced commitment a controlled choice design, and it allows us to address several key questions.  First, does using more structured repayment contracts help pawnshop borrowers to save on financing cost. Second, do borrowers recognize this benefit, demanding commitment in sufficient numbers?  Finally, and most uniquely, because we incorporate the forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment, gaining point identification for the Treatment on the Treated (ToT), the Treatment on the Untreated (TuT), and the average selection on gains.

Our results suggest that the structure of the commitment is strongly effective in preventing default, with the average individual in the forced arm paying financing costs inclusive of fees that are \hl{20\%} lower than the control, while default decreases by 6.5 percentage points (15\% of the mean). In terms of Annual Percentage Rates, the financial cost of borrowing is reduced by 34 percentage points. That is, imposing commitment structure it is possible to save borrowers money by charging them fees! These results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit, using the subjective instead of the gold value of the pawn, and imputing some adjustment for liquidity lost by requiring monthly payments.

The monthly payment contract seems to be achieving these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not, saving the later payments towards recovery. In the treatment group, the first payment occurs 13 days earlier, the fraction recovering on the first visit by is 7.9 percentage point higher. Commitment contract decreases fraction of borrowers making a payment and not recovering by 7 percentage points. Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. Instead, the commitment contract induces people who would otherwise pay something towards recovery to pay more and faster, as well as inducing others who would have made partial payments and anyways defaulted to instead pay nothing.  Both groups save money.

In spite of a large average treatment effect documenting financial cost savings, given the opportunity in the choice arm, only 11\% of borrowers actually choose commitment. If the effect of commitment were homogeneous, this would be enough to conclude that the 89\%
who did not choose it would have been financially better off if they had. However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}. Can the borrowers who did not choose commitment be those who simply don’t need it? We address this question by sequentially imposing more structure in the problem.

We start by bounding the distribution of individual treatment effects as in \cite{fan2010sharp} and find that at least 30\% of individual borrowers benefit from commitment, implying many borrowers did not demand even though the treatment effect would be positive for them. Then, we impose the twin exclusion restrictions necessary for estimation of the ToT and Tut (that the effect of choosing or not choosing is the same as being assigned or not assigned the contract).\footnote{This is a frequently used assumption even if often implicit. For instance, a significant literature uses schooling compulsory laws to estimate the return of one more year of school, and then often interprets that schooling, in general, has this return.}  With these assumptions, both treatment effects are point identified as well as the average selection on gains, average selection on levels, and average selection bias.  Our results indicate that while selection on gains are present in our sample, the financial cost savings of the TuT is still large (at \$356 pesos, it is equivalent to 24 percentage point savings in APR). Hence, on average borrowers that did \textit{not} choose the frequent payment contract would have benefited from having that contract.\footnote{While our estimated ToT is roughly twice the TuT, it is imprecisely estimated due to the low compliance rate, and the hypothesis of ToT=TuT is rejected only with 13 percent confidence for the APR and 12 percent confidence for default.}  We also estimate that those that would not choose if given the opportunity would have lower status-quo outcomes (i.e. the average selection bias is negative). Finally, assuming the exclusion restriction for subsets of observable characteristics splits generated by a causal forest allows us to establish that more than \hl{70\%} of would-be non-choosers would save on financial cost by being assigned to frequent payments. That is, the benefits of imposing a monthly payment are distributed broadly. \hl{TuT benefits are particularly large for XXX CHARACTERISTICS, and ToT benefits for those with XXX.}

@@

What explains the persistence of a contract so contrary to borrowers’ interests?  First, we investigate whether simple impatience could explain the dissonance (our formula for financial does not use discounting, and the contract features near-term costs in return for longer-term benefits).  A simple simulation exercise suggests that at discount rates up to 4,000 percent per annum our core impacts on financial cost remains significantly negative, suggesting that discounting is unlikely to explain our results.  Next, we look at time inconsistent preferences, the workhorse behavioral explanation for the benefits of commitment.  In our context, not only is time inconsistency only a weak driver of selection into commitment, but the TuT of forcing commitment arises almost entirely among those who are \textit{not} time inconsistent.  In this pawnbroking sample we document substantial levels of over-optimism among borrowers, the attribute which we believe explains our results.  Not only do 74\% of borrowers say that they will recover their pawn with perfect certainty (whereas only 43\% actually do), but the impact of forcing on those who would not choose commitment is almost perfectly confined to the sub-sample who reported sure confidence in recovery.   Hence, in this context it appears that the explanation for low demand for commitment among those who benefit arises from an incorrect belief that one has no need to work to avoid default.

@@

%do we want this paragraph on learning?
Does learning eventually overcome the low demand for commitment? For learning to happen clients would need to experiment the frequent payment contract, and this was not the typical contract in the industry. But even if the contract was experienced, borrowers may fail to learn or learn only slowly. We find that those who are forced to the monthly payment product are 6.7 percentage points more likely to become repeat customers than those assigned to the status-quo contract. One way to interpret this is that that having experienced the frequent payment contract (and the lower financial cost of borrowing that come with it), they want to borrow more.\footnote{A second intepretation is that the iliquidity created by the monthly payment contract makes them want obtain second loan to pay the first one. This second explanation is unlikely since borrowers obtain a second loan not within the first 90 days of the first loan when payments are due; moreover, the correlation is also present conditional on having paid down the first loan. Borrowers tend to pledge a different piece for the second loan, so that recovery of the first pawn is also an unlikely explanation.} However, a stronger test of liking the monthly payment contract is whether conditional on coming again, they would choose frequent payments. We test this and we cannot reject that demand is not higher after experiencing the monthly payment contract, however sample sizes are small and \hl{the minimum detectable effect is XXX.}

@@

%Replace this paragraph with discussion of optimal targeting of paternalism
Our results suggest that pawn lending markets capture borrower wealth in ways not well summarized by interest rates. By over-collateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.  Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) may not be adequate. We hesitate to give precise policy recommendations since we don't have good measures of welfare. Even though the monthly payment contract dramatically reduces financial cost, it could potentially generate lower (or higher) anxiety. Moreover, frequent payment requirements may decrease welfare of highly impatient borrowers.\footnote{The paper presents an back of the envelope exercise that suggests annual discount rates of 4000 are necessary to nullify the reductions in financial cost we estimate. \hl{Note also that since the fee for skipping payment is 2\%, the illiquidity imposed by the contract is bounded.}} %Second, given the non-standard nature of the finding, it is likely that we would have to adopt and estimate a particular behavioral model of demand for commitment, which we don't need to do to make the point that TuT is positive.

@@

Second, we join a more nacent literature shedding light into private paternalism. In the context of food choice, \cite{Sprenger} elicit dynamic inconsistencies, and then find that demand for commitment is negatively correlated with such inconsistency. In the context of school choice, \cite{Walters} finds that students that select into more effective schools have smaller treatment effects from attending than those that select out. Besides being very different contexts from ours, we rely on very different methods. In contrast to \cite{Sprenger} we will directly point identify the TuT, obviating the need for elicitation of preferences to test for negative selection. In contrast to \cite{Walters} we use randomization while he needs a structural model and distance to school as an instrument. \hl{FRANK, can I say something more precise than ``a structural model''?}

@@

\paragraph{Most borrowers lose their pawn.} Our context is also one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning. One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default. This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the loan size for 86\% of clients, (c) among those that lose their pawn, 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 74\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.  Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer. Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.

@@

\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the designed of micro-lending contracts, it enhances the regularity and salience of payments as a way to encourage repayment \citep{morduch1999microfinance, bauer2012behavioral}.  It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers. The Commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement). The importance of this monthly payment was made salient in the contract and payment receipts (see Figure \ref{PaperSlip}), and by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments.  The idea that the fee itself is not driving the treatment is reinforced later in the paper where we show financial benefits many times larger than the fee, as well as treatment effects even on those who would fail to recover pawns and hence not pay the fee. Transportation cost to go to the branch to pay is on the same order of magnitude as the fee on average.\footnote{%The lender was worried that if the fee was large, forgetting to pay could make the pawn unrecoverable. 
In contrast with \cite{John} we don't let the clients choose the size of the fee. \cite{John} shows that doing this results in costly choices by (partially) naive present biased consumers. Our fee is much smaller than the median in her experiment. %We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.
} To elicit demand for the monthly payment contract, we include an arm that allows borrowers to opt into this contract if they choose. The existence of both a non-optional ``forcing'' arm, and a choice arm in our design is key to estimate a battery of treatment effects above an average treatment effect under fairly mild assumptions.

@@

@@

we estimate a flexible model of take-up of the commitment-fee contract \textit{in the Choice arm} using gradient boosting classification\footnote{Results are robust to other classification methods like Random Forest, SVM, etc.} and obtain for a client with characteristics $x_i$ a calibrated probability $P(x_i)$ of choosing the commitment contract.

@@

\todo[inline]{Add a column with losing pawn. What about re-pawning?}
\todo[inline]{How did we decide to deal with censoring?}

@@

\todo[inline]{I think the re-pawn table should only have 4 columns. Remove variables 3,4, and 7. In terms of the order: keep column 1, make 5 and 6  the new columns 2 and 3, and make the current column 2 the new column 4. I am goint to write the paragraphs assuming this.}

@@

\subsection{Censoring of Loan Completion}

>>>>

\title{The controlled choice design and private paternalism in pawnshop borrowing\thanks{We want to thank Mauricio Romero and Anett John for advice and encouragement. Ricardo Olivares, Gerardo Melendez, and Alonso de Gortari provided excellent research assistance and Erick Molina helped with formatting. Jose Maria Barrero, Andrei Gomberg, Emilio Gutierrez, David Laibson, Aprajit Mahajan, Matt Rabin, Charlie Sprenger, and seminar participants at ITAM, USC, MSU, and UCSD provided valuable feedback.}}
\author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia   \thanks{Seira: ITAM/MSU, \url{enrique.seira@gmail.com} (corresponding author); McIntosh:  University of California San Diego, \url{ctmcintosh@ucsd.edu}; Meza: Harvard University, \url{isaacmezalopez@g.harvard.edu}; Sadka: ITAM, \url{jsadka@itam.mx}; DiTraglia: Oxford, \url{francis.ditraglia@economics.ox.ac.uk}} }
\date{This draft:  \today \\[2 cm]}

@@

Substantiating a case for private paternalism is not easy. It involves comparing the causal effect of forcing a certain product characteristic versus the effect of letting people choose it. Because choice may be correlated with unobservables, identification 
is challenging in observational studies.  %This is not a straightforward task because choice will be driven by unobservable factors, and to address the question fully 
Moreover, to have a complete picture of the benefits of forcing, one would want a counterfactual for the outcome of both choosers and non-choosers. A large behavioral literature has illustrated that allowing borrowers or savers to choose commitment-style products increase savings in an Intention-to-Treat sense \citep{thaler2004save, prina2015banking, brune2016facilitating, callen2019headwaters, Pascaline, Ashraf}, but this literature has rarely inquired about the benefits of imposing commitment.\footnote{Selection on gains has such wide acceptance that economists often impose it in their models (for example, in the study of migration \cite{chiquiar2005international} and occupational choice \cite{heckman1990empirical}. In microfinance, a context close to ours, \citep{Murdoch} claims that positive selection exists, citing a positive correlation between displaying present biased preferences in surveys and selecting into microfinance as evidence of borrowers' actually demanding the discipline imposed by frequent payments.}  In this paper we illustrate how a three-armed, `controlled choice' design can be used to form counterfactuals for both choosers and non-choosers of commitment. We implement such a design in a high-stakes and policy-relevant environment, enabling us to test selection-on-gains as well as isolating the impact of paternalistic policies.

@@

We study the benefits of private paternalism in the context of pawnbroker lending. Pawn loans are one of the oldest, most understudied, and most prevalent forms of borrowing \citep{carter2012pawnshops}. There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a 43 billion dollar industry).\footnote{\url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.} Our partner pawn lender (henceforth Lender $P$) alone served more than 1 million clients in the last 3 years with more than 4 million contracts.\footnote{For comparison there were 2.3 million micro-finance clients in Mexico in 2009 (\cite{Pedroza:2010}).} Pawnshop lending presents an inverted lending case: since these loans are over-capitalized, the principal in the lending contract stands to gain the most when agents default.

Our collaborating pawn lender (henceforth Lender P) gave 70\% of the value of the pawn in credit, and charged a monthly interest rate of 7\% for loans of a three-month duration, with a flexible no-reminders contract typical of the industry that can be paid back anytime before the loan comes due at no penalty. We call this the status-quo contract. This combination of features, and the fact that the gold pawn is highly liquid, means that the lender makes 90\% more profit over three months for a borrower who defaults than one who repays (30\% of collateral value recovered under default, 15.8\% of collateral value paid in interest if loan fully repaid). While an older literature considers the exploitative potential in over-collateralization and underpricing of collateral \citep{basu1984implicit}, the implication of such contracts has not been analyzed in the behavioral literature.  %When the lender desires default, the repayment-inducing features of commitment-style repayment contracts become undesirable and there may be incentives for the principal to create contracts with no structure, no reminders, and simple balloon payments. 
To repurpose the language of \cite{Laibson2018}, we suggest that pawn contracts effectively shroud their \textit{lack} of commitment features to induce default in a manner not obvious to borrowers. Given that pawnshops, moneylenders, and paycheck lending institutions are likely to face client pools disproportionately made up of impatient and time-inconsistent individuals, the design of such contracts may have serious consequences for the financial lives of the poor.

@@

Against this backdrop, we implement a multi-arm randomized control trial covering close to 10,000 pawnshop clients in 6 branches of Lender $P$ in Mexico City, using a design built to test the demand for and impact of payment structure in pawn repayment contracts. Our control arm illustrates the costs of the status quo contract; fully \textcolor{blue}{56\%} of borrowers default and so lose their pawn.\footnote{These high default rates are not uncommon, in the US default is also high at 15\% (\url{https://tinyurl.com/yc2x5bjf}).} We then implement a `commitment choice’ arm, in which borrowers are able at the time of taking a loan to opt into a structured repayment contract, in which they are asked to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time, and borrowers levied a nominal fee of 2\% of that month's payment in case of delinquency as a reminder/reinforcement of the importance of these interim payments. In addition, we include a `forced commitment’ arm, in which all borrowers are required to repay using the monthly payment structure. We will use the terms monthly payments, structured payments, and commitment contract interchangeably.

We call this randomization of voluntary and forced commitment a controlled choice design, and it allows us to address several key questions.  First, does using more structured repayment contracts help pawnshop borrowers to save on financing cost. Second, do borrowers recognize this benefit and demand commitment? % demanding commitment in sufficient numbers?  
Finally, and most uniquely, because we incorporate the forced commitment arm, we are able to ask whether the \textit{right} borrowers voluntarily demand commitment, gaining point identification for the Treatment on the Treated (ToT), the Treatment on the Untreated (TuT), and the average selection on gains.

Our results suggest that the structure of the commitment is strongly effective in preventing default, with the average individual in the forced arm paying financing costs inclusive of fees that are \hl{20\%} lower than the control, while default decreases by 6.5 percentage points (15\% of the mean). In terms of Annual Percentage Rates, the financial cost of borrowing is reduced by 34 percentage points. That is, imposing a commitment structure it is possible to save borrowers money by charging them fees. These results are robust qualitatively to including transport costs of going to the branch plus losing a day's wage for each visit, using the subjective instead of the gold value of the pawn, and imputing some adjustment for liquidity lost by requiring monthly payments.

The monthly payment contract seems to be achieving these cost savings by speeding up payments and by generating an early bifurcation of borrowers into those that will recover the pawn and those that will not, saving the later payments towards recovery (which are lost in the case of default). In the treatment group, the first payment occurs 13 days earlier, and the fraction recovering on the first visit by is 7.9 percentage points higher. The commitment contract also decreases fraction of borrowers making a payment and not recovering by 7 percentage points. Treatment effects are concentrated in the intensive margin as treatment does not affect the fraction of clients who pay a positive amount towards pawn recovery. Instead, the commitment contract induces people who would otherwise pay something towards recovery to pay more and faster, as well as inducing others who would have made partial payments and anyways defaulted to instead pay nothing.  Both groups save money.

In spite of a large average treatment effect documenting financial cost savings, given the opportunity in the choice arm, only 11\% of borrowers actually choose payment structure. If the effect of payment structure were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had. However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}. Can the borrowers who did not choose commitment be those who simply don’t need it? We address this question by sequentially imposing more structure in the problem.

We start by not imposing assumptions and bounding the distribution of individual treatment effects as in \cite{fan2010sharp}. Using bounds we find that at least 30\% of individual borrowers benefit from commitment, implying many borrowers did not demand the structured payment contract even though the treatment effect would be positive for them. Then, we impose the twin exclusion restrictions necessary for estimation of the ToT and TuT ---that the effect of choosing or not choosing is the same as being assigned or not assigned the contract, i.e. that the act of choosing itself is irrelevant.\footnote{This is a frequently used assumption even if often implicit. For instance, a significant literature uses schooling compulsory laws to estimate the return of one more year of school, and then often interprets that schooling, in general, has this return.}  With these assumptions, both treatment effects are point identified, as is the average selection on gains, the average selection on levels, and the average selection bias.  Our results indicate that while selection on gains are present in our sample, the financial cost savings of the TuT is still large (at \$356 pesos, it is equivalent to 24 percentage point savings in APR). Hence, on average borrowers that did \textit{not} choose the frequent payment contract would have benefited from having that contract.\footnote{While our estimated ToT is roughly twice the TuT, it is imprecisely estimated due to the low compliance rate, and the hypothesis of ToT=TuT is rejected only with 13 percent confidence for the APR and 12 percent confidence for default.}  We also estimate that those that would not choose if given the opportunity would have lower status-quo outcomes (i.e. the average selection bias is negative). Finally, assuming the exclusion restriction for subsets of observable characteristics splits generated by a causal forest allows us to establish that more than \hl{70\%} of would-be non-choosers would save on financial cost by being assigned to frequent payments. That is, the benefits of imposing a monthly payment are distributed broadly. \hl{TuT benefits are particularly large for XXX CHARACTERISTICS, and ToT benefits for those with XXX.}

@@

What explains the persistence of a contract so contrary to borrowers’ interests?  First, we investigate whether simple impatience could explain the dissonance (our formula for financial does not use discounting, and the contract features near-term costs in return for longer-term benefits).  A simple simulation exercise suggests that at discount rates up to 4,000 percent per annum our core impacts on financial cost remains significantly negative, suggesting that discounting is unlikely to explain our results.  Next, we look at time inconsistent preferences, the workhorse behavioral explanation for the benefits of commitment.  In our context, not only is time inconsistency only a weak driver of selection into commitment, but the TuT of forcing commitment arises almost entirely among those who are \textit{not} time inconsistent.\footnote{\textcolor{blue}{Although telling, we acknowledge that our measure of present bias is simple (as its survey-based and the survey was necessarily short). For this reason this result needs to be interpreted with care.}}  In this pawnbroking sample we document substantial levels of over-optimism among borrowers, and it has predictive power for our results. %which we believe explains our results. 
Not only do 74\% of borrowers say that they will recover their pawn with perfect certainty (whereas only 43\% actually do), but the impact of forcing on those who would not choose commitment is almost perfectly confined to the sub-sample who reported sure confidence in recovery. Hence, in this context it appears that the explanation for low demand for commitment among those who benefit arises from an incorrect belief that one has no need to work to avoid default.

@@

%do we want this paragraph on learning?
Does learning eventually overcome the low demand for commitment? For learning to happen clients would need to experiment the frequent payment contract, and this was not the typical contract in the industry. But even if the contract was experienced, borrowers may fail to learn or learn only slowly. We find that those who are forced to the monthly payment product are 6.7 percentage points more likely to become repeat customers than those assigned to the status-quo contract. One way to interpret this is \textcolor{blue}{as `learning they like pawn-borrowing', i.e. having experienced the frequent payment contract (and the lower financial cost of borrowing that come with it), they like pawning and pawn more.}\footnote{A second intepretation is that the iliquidity created by the monthly payment contract makes them want obtain second loan to pay the first one. This second explanation is unlikely since borrowers obtain a second loan not within the first 90 days of the first loan when payments are due; moreover, the correlation is also present conditional on having paid down the first loan. Borrowers tend to pledge a different piece for the second loan, so that recovery of the first pawn is also an unlikely explanation. \textcolor{blue}{A different test, about `learning they like monthly-payments'} is whether conditional on coming again, clients would choose frequent payments. We test this and we cannot reject that demand is \textit{not} higher after experiencing the monthly payment contract, \textcolor{blue}{consistent with no learning or slow learning that the monthly payment contract is better than the status quo contract}, however sample sizes are small and \hl{the minimum detectable effect is XXX.}} %\textcolor{blue}{making this more rigorous test of learning inconclusive and left for future research. Having said this, after more than 100 years in operation, the biggest pawn lender in Mexico and most others still do not offer structured payment contracts.}

@@

%Replace this paragraph with discussion of optimal targeting of paternalism
Our results suggest that pawn lending markets capture borrower wealth in ways not well summarized by interest rates. By over-collateralizing and then structuring loan contracts in a manner encouraging of default, lenders are able to extract substantial value independent of the interest charged.  Further, the `nudge’ approach generally favored by the behavioral literature (voluntary commitment) may not be adequate. We hesitate to give precise policy recommendations since we don't have good measures of welfare. Even though the monthly payment contract dramatically reduces financial cost, it could potentially generate lower (or higher) anxiety. Moreover, frequent payment requirements may decrease welfare of highly impatient borrowers.\footnote{The paper presents an back of the envelope exercise that suggests annual discount rates of 4000 are necessary to nullify the reductions in financial cost we estimate. \hl{Note also that since the fee for skipping payment is 2\% of the payment due, the illiquidity imposed by the contract is bounded.}} %Second, given the non-standard nature of the finding, it is likely that we would have to adopt and estimate a particular behavioral model of demand for commitment, which we don't need to do to make the point that TuT is positive.

@@

Second, we join a more nacent literature shedding light into private paternalism. In the context of food choice, \cite{Sprenger} elicit dynamic inconsistencies, and then find that demand for commitment is negatively correlated with such inconsistency. In the context of school choice, \cite{Walters} finds that students that select into more effective schools have smaller treatment effects from attending than those that select out. Besides being very different contexts from ours, we rely on very different methods. In contrast to \cite{Sprenger} we will directly point identify the TuT, obviating the need for elicitation of preferences to test for negative selection. In contrast to \cite{Walters} we use randomization while he needs a structural model and distance to school as an instrument. \todo[inline]{FRANK, can we say something more precise than ``a structural model''?}

@@

\paragraph{Most borrowers lose their pawn.} Our context is also one with high borrower default: \hl{60\%} of clients lose their pawn in a time span of 230 days from the date of pawning. One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default. This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the loan size for 86\% of clients, (c) among those that lose their pawn, 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 74\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.  Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer. Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.

@@

\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the designed of micro-lending contracts, it enhances the regularity and salience of payments as a way to encourage repayment \citep{morduch1999microfinance, bauer2012behavioral}.  It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers. The Commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement). The importance of this monthly payment was made salient in the contract and payment receipts (see Figure \ref{PaperSlip}), and by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments.  The idea that the fee itself is not driving the treatment is reinforced later in the paper where we show financial benefits many times larger than the fee, as well as treatment effects even on those who would fail to recover pawns and hence not pay the fee. Transportation cost to go to the branch to pay is on the same order of magnitude as the fee on average.\footnote{%The lender was worried that if the fee was large, forgetting to pay could make the pawn unrecoverable. 
%In contrast with \cite{John} we don't let the clients choose the size of the fee. \cite{John} shows that doing this results in costly choices by (partially) naive present biased consumers. Our fee is much smaller than the median in her experiment. 
} To elicit demand for the monthly payment contract, we include an arm that allows borrowers to opt into this contract if they choose. The existence of both a non-optional ``forcing'' arm, and a choice arm in our design is key to estimate a battery of treatment effects above an average treatment effect under fairly mild assumptions.

@@

A natural starting point for understanding the role of voluntary commitment is the determinants of choice.  Figure \ref{determinants_choose} provides coefficient plots for univariate and multivariate Linear Probability Models explaining takeup of commitment in the Choice arm.  Contrary to the standard behavioral motivations, none of our measures of self control predict takeup, neither the metric arising from the paired discounting questions (e.g. those who are more impatient over immediate rather than future delays), nor a simple survey question asking whether they are tempted to mis-use money in their financial lives.  Individuals who report having trouble paying bills are actually \textit{less} likely to take commitment, as are those who have pawned before.  The only determinant in this figure that represents something like sophistication is that those with more education are more likely, in both univariate and multivariate regressions, to choose commitment.  Overall, we observe few strong determinants of commitment choice and the story does not appear to be a behavioral one.

@@

@@

%\todo[inline]{Add a column with losing pawn. What about re-pawning?}
%\todo[inline]{How did we decide to deal with censoring?}

@@

%\todo[inline]{I think the re-pawn table should only have 4 columns. Remove variables 3,4, and 7. In terms of the order: keep column 1, make 5 and 6  the new columns 2 and 3, and make the current column 2 the new column 4. I am goint to write the paragraphs assuming this.}

@@

%\subsection{Censoring of Loan Completion}

\paragraph{Censoring of Loan Completion.} The window of time during which we were able to observe borrower behavior was limited in each branch, meaning that there were loans that we do not see completed (particularly those pawns that were rolled over for one or two further 90-day spells).  Overall, \hl{XX\%} of all experimental loans are censored, meaning that they neither default nor repaid within the observation window.  In the prior analysis we handle this issue by using outcomes such as `did not default' which are defined even when we do not observe the completion of the loan, and only considering costs that we observe directly.  We have also showed, however, that one effect of the forcing arm is to accelerate repayment, meaning that it is less likely for loans in this arm to be censored.  This issue is illustrated in Figure \ref{survival_graph}, which shows the CDF of loan completion (Panel (a)) and loan recovery (Panel (b)) by the number of days since first pawn.  Two features of these graphs are salient for our analysis.  The first is the extent to which loan outcomes are observed more quickly in the forcing arm.  This is primarily due to the the substantially higher rate of repayment of Forced Commitment loans at 120 days ($\sim$15 pp higher than the other arms).  The second is the very low rate at which loans are recovered in any arm after 120 days.  In the 180 day window after the second rollover period we see a further $\sim$10 percent of loans repaid in all arms, but these loans are largely dormant, suggesting that many of the censored loans will in fact be defaulted upon.

The approach taken so far is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the forced commitment arm does not translate mechanically into a treatment effect on default. \textcolor{blue}{Appendix \ref{App_censoring} imputes default predictions for censored loans and also performs a bounding exercise and reaches similar conclusions.}
%The confluence of censoring and a treatment effect on censoring is problematic from an experimental point of view.
